Learning Auditory Similarities Between Instrumental Playing Techniques

### 2018-01-29 paper/lagrangeSpontaneousSimilarity2017.tex
comment on figure 8

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/frame.png}
\caption{Spatial and group organization provided by subject 1.}
\label{fig:frame}
\end{figure}

@@

>>>>

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/frame.png}
\caption{Spatial and group organization provided by subject 1.
\vl{This caption is obviously wrong, as it was copied verbatim from Figure 1. The x axis should be made logarithmic, which uneven tick marks.
The legend is difficult to understand (acronyms, subtle difference between "multiple" and "consensus").
Again, the legend box could be removed after placing the labels next to the lines themselves. @figure}}
\label{fig:frame}
\end{figure}

@@

\vl{Let's use the gender-neutral singular "they" instead of "he".@writing}
